---
title: "Report for ACME"
author: "Csaba Bakonyvari"
date: "`r format(Sys.Date())`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is an imaginary situation. I analyzed the population distribution of three selected countries (Japan, Russia and the United Kingdom) by blood type for an imaginary pharmacological research.

The original data was obtained from https://en.wikipedia.org/wiki/Blood_type_distribution_by_country

#I am using the following libraries:

```{r loading-libs, message=FALSE}
library(tidyverse)
library(ggplot2)
```
  
#There are a couple of more row of code what I can show if I want:

```{r}
load("rda/tidy-blood-type-table.rda")
load("rda/pop-blood-type-table.rda")

country_filter <- c("Japan","Russia", "United Kingdom")

filtered_tidy_blood_type <- tidy_blood_type %>% 
  filter(Country %in% country_filter)

filtered_pop_blood_type <- pop_blood_type %>%
  filter(Country %in% country_filter)

#class check
filtered_tidy_blood_type$Country <- as.factor(filtered_tidy_blood_type$Country)
filtered_tidy_blood_type$Blood_Type <- as.factor(filtered_tidy_blood_type$Blood_Type)
filtered_pop_blood_type$Country <- as.factor(filtered_pop_blood_type$Country)
```

## Blood type distribution by country

This is a barplot showing the ABO distributions in the selected countries.
In this case I am hiding the related code. You can only see the plot.

```{r blood type distribution by country, echo=FALSE}
filtered_tidy_blood_type %>%
  ggplot(aes(Country, Percentage, col = Country)) +
  geom_bar(stat = "identity", width = 0.5) +
  facet_grid(~Blood_Type) +
  theme(axis.text = element_text(angle = 90, hjust = 1), legend.position = "none") +
  xlab("") +
  ylab("% of population") +
  ggtitle("ABO distribution in Japan, Russia and the United Kingdom")
```
